Figures

### 2019-04-29 figures/07_model-selection.Rmd
towards posterior summaries

# linear
model_form <- bf(tp ~ agvpct)

# linear re
model_form <- bf(tp ~ (1 + agvpct | hu4vzoneid))

@@

# non-linear re w/ 2nd level coeffs
model_form2 <- bf(tp ~ bagvpct * agvpct, 
                 bagvpct ~ 1 + phosphorusvfertilizervuse + soybeans +
                   (1|hu4vzoneid), 
                 nl = TRUE)
fit2 <- brm(formula = model_form2, data = dt, 
           family = gaussian())
---
loo1 <- loo(fit1)
loo2 <- loo(fit2)
loo_compare(loo1, loo2)

>>>>

# linear
# model_form <- bf(tp ~ agvpct)

# linear re
model_form <- bf(tp ~ (1 + agvpct | hu4vzoneid))
fit <- brm(formula = model_form, data = dt, 
           family = gaussian())

@@

# non-linear re w/ 2nd level coeffs
model_form2 <- bf(tp ~ bagvpct * agvpct, 
                 bagvpct ~ 1 + phosphorusvfertilizervuse + soybeans +
                   (1|hu4vzoneid), 
                 nl = TRUE)
fit2 <- brm(formula = model_form2, data = dt, 
           family = gaussian())
---

# plot(fit1, pars = "bagvpct")

get_variables(fit)
spread_draws(fit, b_Intercept)

test <- spread_draws(fit, r_hu4vzoneid[hu4vzoneid,term]) %>%
  dplyr::filter(term == "agvpct" & hu4vzoneid == "HU4_40")

m <- add_fitted_draws(dt, b_)

spread_draws(fit, Intercept)
spread_draws(fit1, bagvpct[hu4vzoneid,])

ggplot() + 
    stat_lineribbon(data = m, 
                             aes(x = retention_time_yr, 
                                 y = estimate), .prob = c(0.95), 
                    fill = "grey", color = "black", alpha = 0.5)

+ 
    geom_point(data = nes, aes(x = retention_time_yr, 
                               y = p_percent_retention), 
               size = 0.6, color = "black") + 
    scale_x_log10() + ylim(0, 1) +
    scale_fill_discrete("grey") + 
    theme_pred() + 
ylab("P retention") + xlab("Residence time (yr)") + ggtitle("A.")

stat_lineribbon()
stancode(fit1)

m <- tidybayes::recover_types(fit1)

bayes_results = m %>%
  spread_draws()
%>%
  median_qi(estimate = condition_mean) %>%
  to_broom_names() %>%
  mutate(model = "Bayes")
bayes_result

---
loo1 <- loo(fit1)
loo2 <- loo(fit2)
loo_compare(loo1, loo2)  
---
